---
title: "CREAHIA: Philippines example"
output: github_document
vignette: >
  %\VignetteIndexEntry{example_philippines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# Installation
```{r, eval = FALSE}
library(remotes)
remotes::install_github("energyandcleanair/creahia")
```

```{r,  message=FALSE}
library(creahia)
```

Configuration:
```{r}
calpuff_dir <- "../examples/example_ph"
gis_dir <- "/Volumes/ext1/gis/" # Where to find baseline concentration etc. Contact-us to have access to the required data
```

# Create concentration fields

To perform an health impact assessment, `creahia` requires:
- `conc_scenario`: the concentration field of one or several species in one or several scenarios for which we want to evaluate the health impact
- `conc_baseline`: the baseline concentration of the selected species.

We also define `conc_perturbation` such that `conc_scenario = conc_baseline + conc_perturbation`.

## Read CALPUFF results
```{r, cache=TRUE, message=FALSE, warning=FALSE}
conc_perturbation <- creahia::get_conc_calpuff(calpuff_dir=calpuff_dir, utm_zone=51, utm_hem='N', map_res=1)

species <- unique(conc_perturbation$species)
scenarios <- unique(conc_perturbation$scenario)
grid_raster <- conc_perturbation$conc_perturbation[[1]] %>% raster::raster()
grid_raster
```
Plot pm25 perturbation:
```{r, fig.fullwidth=TRUE}
conc_pm25 <- conc_perturbation[conc_perturbation$species=="pm25",]
rs <- raster::stack(conc_pm25$conc_perturbation)
names(rs) <- paste(conc_pm25$scenario, conc_pm25$species, sep=" - ")
raster::plot(rs)
```

## Read baseline concentrations
```{r, cache=TRUE}
conc_baseline <- creahia::get_conc_baseline(species=species, grid_raster=grid_raster)
conc_baseline
```


## Combine both
```{r, cache=TRUE}
concs <- creahia::combine_concs(conc_perturbation, conc_baseline) %>%
  flatten_concs() %>% # Make it one row per scenario
  add_pop() # Add popilation data
```

## Select regions of interest
We select regions of interest from GADM dataset, at the administrative level 2.
```{r, message=FALSE, cache=TRUE}
regions <- creahia::get_adm(grid_raster, admin_level=2)
regions <- regions[1:5,] # For example purposes, we only keep a subset
```

and extract concentrations there:
```{r, cache=TRUE}
conc_regions <- creahia::extract_concs_at_regions(concs, regions)
```

# Health Impact Assessment
```{r, cache=TRUE, message=FALSE}
hia <- compute_hia(conc_map=conc_regions,
                   species=species,
                   regions=regions)
hia
```

Summarise HIA:
```
hia_table <- hia %>% totalise_hia() %>% make_hia_table()
hia_table
```
